Replacing handwritten signatures with open electronic signature software

### 2020-05-18 paper/main.tex
Add final changes to the paper and info about thesis submission

We also support adding a visible signature for PDFs.
This helps users to recognize it was digitally signed without a need to mention it in the document itself and provides information on who or when signed it.
Labels are translated using the current language of the application as we assume this will be the language the receiver will most likely speak.

@@

To improve on this further, we are doing a \pojem{code-signing} for each release using a trusted way for each platform.
On macOS, this means enrolling in the Apple Developer Program that requires an annual fee and installation of signing certificates.
Additionally, it is necessary to \textit{notarize} the application for use on macOS.
Notarization is an automated process required by Apple to prove that the application does not contain any malicious code and is properly signed and configured.
If the application is not notarized, Gatekeeper will warn the user about the potentially unsafe software.
On modern versions of Windows, applications that are not code-signed can trigger a warning or, depending on the settings, even completely prevent the user from using software that is not code-signed using a certificate that is cosigned with a trusted root certificate.
Certification for individuals on the macOS seems to be fully automated, does not involve lengthy verification, and costs 99 USD a year.
Certification on Windows is offered by various trusted third parties like DigiCert.com that we have used and involves lengthy, partially automated verification at a price starting from 60 USD a year.
At the time of writing, there does not seem to be any service offering code-signing certificates to OSS for free.

>>>>

\iffalse % This was not yet stable at the time of publishing
We also support adding a visible signature for PDFs.
This helps users to recognize it was digitally signed without a need to mention it in the document itself and provides information on who or when signed it.
Labels are translated using the current language of the application as we assume this will be the language the receiver will most likely speak.
\fi

@@

To improve on this further, we tried to do a \pojem{code-signing} for each release using a trusted way for each platform.
On macOS, this means enrolling in the Apple Developer Program that requires an annual fee and installation of signing certificates.
Additionally, it is necessary to \textit{notarize} the application for use on macOS.
Notarization is an automated process required by Apple to prove that the application does not contain any malicious code and is properly signed and configured.
If the application is not notarized, Gatekeeper will warn the user about the potentially unsafe software.
On modern versions of Windows, applications that are not code-signed can trigger a warning or, depending on the settings, even completely prevent the user from using software that is not code-signed using a certificate that is cosigned with a trusted root certificate.
Certification for individuals on the macOS seems to be fully automated, does not involve lengthy verification, and costs 99 USD a year.
Certification on Windows is offered by various trusted third parties like DigiCert.com that we have used and involves lengthy, partially automated verification at a price starting from 60 USD a year.
At the time of writing, there does not seem to be any service offering code-signing certificates to OSS for free.
We were not able to finish the process on time for the publishing of this thesis - we feel like this process could be improved in the future for OSS.
